---
title: "R_project_JClab_Fall2016"
author: "ITG, JL"
date: "December 3, 2016"
output: html_document
---
##Sidenote
This document will record the progress and scripts used to analyze growth curve data from our research lab.

##Materials: Raw data from spectrophotometer
Spectrophotometer provided .xlsx files for raw data. Datasheets were converted to .csv and .txt for analysis in Rstudio.
One 96-well plate named "161011 Rm1021 jspA kinetic A600 HTX linear edited.xlsx" containing four replicates of data.
File was converted to .csv for analysis in R.
Data was seperated depending on genotypes expressed.
##Methods: Plotting growth curves on Rstudio with ggplot2
Install packages for analysis
```{r}
install.packages('ggplot2')
library(ggplot2)
```
Save .csv files as variable.
```{r}
csv_161011_vectors<-read.csv("csv_161011 Rm1021 jspA kinetic A600 HTX linear edited_vector.csv")
csv_161011_jspA<-read.csv("csv_161011 Rm1021 jspA kinetic A600 HTX linear edited_jspA.csv")
csv_161011_jspA_E148A<-read.csv("csv_161011 Rm1021 jspA kinetic A600 HTX linear edited_jspA E148A.csv")
csv_161011_jspA_E148A_HA<-read.csv("csv_161011 Rm1021 jspA kinetic A600 HTX linear edited_jspA E148A-HA.csv")
csv_161011_jspA_HA<-read.csv("csv_161011 Rm1021 jspA kinetic A600 HTX linear edited_jspA-HA.csv")
```
Plot data on to graphs for visualization. 
```{r}
vector_ggplot <- ggplot(csv_161011_vectors, aes(x = Time, y = OD, color=Genotype)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: Vector") + ylim (0,0.35)
jspA_ggplot <- ggplot(csv_161011_jspA, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA overexpression") + ylim (0,0.35)
jspA_E148A_ggplot <- ggplot(csv_161011_jspA_E148A, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA(E148A) overexpression") + ylim (0,0.35)
jspA_E148A_HA_ggplot <- ggplot(csv_161011_jspA_E148A_HA, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA(E148A)-HA overexpression") + ylim (0,0.35)
jspA_HA_ggplot <- ggplot(csv_161011_jspA_HA, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA-HA overexpression") + ylim (0,0.35)
```
Subset data for exponential growth phase.
```{r}
csv_161011_vector_subset <- subset(csv_161011_vectors, Time >= 300 & Time <= 1000, select = c(Time, OD, Genotype))
csv_161011_jspA_subset <- subset(csv_161011_jspA, Time >= 300 & Time <= 1000, select = c(Time, OD, Genotypes))
csv_161011_jspA_E148A_subset <- subset(csv_161011_jspA_E148A, Time >= 300 & Time <= 1000, select = c(Time, OD, Genotypes))
csv_161011_jspA_HA_subset <- subset(csv_161011_jspA_HA, Time >= 300 & Time <= 1000, select = c(Time, OD, Genotypes))
csv_161011_jspA_E148A_HA_subset <- subset(csv_161011_jspA_E148A_HA, Time >= 300 & Time <= 1000, select = c(Time, OD, Genotypes))
```
Create ggplot graphs of subsetted data.
```{r}
vector_ggplot_subset <- ggplot(csv_161011_vector_subset, aes(x = Time, y = OD, color=Genotype)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: Vector") + ylim (0,0.35)
jspA_ggplot_subset <- ggplot(csv_161011_jspA_subset, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA overexpression") + ylim (0,0.35)
jspA_E148A_ggplot_subset <- ggplot(csv_161011_jspA_E148A_subset, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA(E148A) overexpression") + ylim (0,0.35)
jspA_HA_ggplot_subset <- ggplot(csv_161011_jspA_HA_subset, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA-HA overexpression") + ylim (0,0.35)
jspA_E148A_HA_ggplot_subset <- ggplot(csv_161011_jspA_E148A_HA_subset, aes(x = Time, y = OD, color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "OD600") + ggtitle("OD vs Time: jspA(E148A)-HA overexpression") + ylim (0,0.35)
```
Create new column for log growth.
```{r}
csv_161011_vector_subset["log(OD)"] <- log(csv_161011_vector_subset$OD)
csv_161011_jspA_subset["log(OD)"] <- log(csv_161011_jspA_subset$OD)
csv_161011_jspA_E148A_subset["log(OD)"] <- log(csv_161011_jspA_E148A_subset$OD)
csv_161011_jspA_HA_subset["log(OD)"] <- log(csv_161011_jspA_HA_subset$OD)
csv_161011_jspA_E148A_HA_subset["log(OD)"] <- log(csv_161011_jspA_E148A_HA_subset$OD)
```
Graph log(OD) versus time
```{r}
log_vector_ggplot_subset <- ggplot(csv_161011_vector_subset, aes(x = Time, y = log(OD), color=Genotype)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "log(OD600)") + ggtitle("log(OD) vs Time: Vector")
log_jspA_ggplot_subset <- ggplot(csv_161011_jspA_subset, aes(x = Time, y = log(OD), color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "log(OD600)") + ggtitle("log(OD) vs Time: jspA overexpression")
log_jspA_E148A_ggplot_subset <- ggplot(csv_161011_jspA_E148A_subset, aes(x = Time, y = log(OD), color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "log(OD600)") + ggtitle("log(OD) vs Time: jspA(E148A) overexpression")
log_jspA_HA_ggplot_subset <- ggplot(csv_161011_jspA_HA_subset, aes(x = Time, y = log(OD), color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "log(OD600)") + ggtitle("log(OD) vs Time: jspA-HA overexpression")
log_jspA_E148A_HA_ggplot_subset <- ggplot(csv_161011_jspA_E148A_HA_subset, aes(x = Time, y = log(OD), color=Genotypes)) + geom_point(size=1) + labs(x= "Time(minutes)", y= "log(OD600)") + ggtitle("log(OD) vs Time: jspA(E148A)-HA overexpression")
```
Find intercept and slope and add trendline to ggplot graph
```{r}
coef(lm(log(OD) ~ Time, data = csv_161011_vector_subset))
log_vector_ggplot_subset + geom_abline(intercept = -2.617028066, slope = 0.001556344)
```
